Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalnew\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-06-22 ms.tex

In \paperit, only parameters directly observable from the \KT\ light curve
itself were reported: the period, time of transit center, and transit depth.
With stellar properties now in hand, we can convert these observational
results into fundamental parameters of each planet candidate.
For each candidate, we fit the light curve using a physical transit model
\citep{Mandel02, Kipping10b} simultaneously with the systematics model
described by \paperit.
We use \texttt{emcee} \citep{Foreman-Mackey12}, an implementation of the
affine-invariant ensemble sampler of \citet{Goodman10}
 to sample from the posterior probability distribution
for the stellar---limb darkening coefficients, mass, radius, and effective
temperature---and planetary---radius, period, phase, impact parameter,
eccentricity, and argument of periapsis---parameters, conditioned on the
light curve and the measured stellar properties.
Following \paperit, the likelihood function that we use is marginalized over
the parameters of the systematics model.

@@

\acknowledgements
We thank Roberto Sanchis-Ojeda (Berkeley), Dan Huber (Sydney) and
Jeff Coughlin (SETI) for
conversations and suggestions which improved the quality of this manuscript.
\change{We also thank Keivan Stassun (Vanderbilt) for his insights into 
 stellar parameters for both \kep\ and \KT, which significantly improved
 this work.
We thank the anonymous referee for their insightful comments as well.}

>>>>

In \paperit, only parameters directly observable from the \KT\ light curve
itself were reported: the period, time of transit center, and transit depth.
With stellar properties now in hand, we can convert these observational
results into fundamental parameters of each planet candidate.
For each candidate, we fit the light curve using a physical transit model
\citep{Mandel02, Kipping10b} simultaneously with a systematics model similar
to the one described by \paperit.
We use \texttt{emcee} \citep{Foreman-Mackey12}, an implementation of the
affine-invariant ensemble sampler of \citet{Goodman10}
 to sample from the posterior probability distribution
for the stellar---limb darkening coefficients, mass, radius, and effective
temperature---and planetary---radius, period, phase, impact parameter,
eccentricity, and argument of periapsis---parameters, conditioned on the
light curve and the measured stellar properties.

\change{%
Following \paperit, the likelihood function that we use is marginalized over
the weights of the ``eigen light curves'' in the linear systematics model.
Unlike \paperit, we include an empirical Gaussian prior on the weights
determined by robustly computing the distribution of weights across the full
set of Campaign~1 light curves.
This prior mitigates the incorrect detection of false signals induced by
stellar variability---as discussed below in Section~\ref{sec:systematics}---so
we exclude these candidates (EPIC 201929294 and EPIC 201555883) from the Table
of results.
}

@@

\acknowledgements
We thank Roberto Sanchis-Ojeda (Berkeley), Dan Huber (Sydney) and
Jeff Coughlin (SETI) for
conversations and suggestions which improved the quality of this manuscript.
\change{We also thank Keivan Stassun (Vanderbilt) for his insights into
 stellar parameters for both \kep\ and \KT, which significantly improved
 this work.
We thank the anonymous referee for their comments and suggestions.}
